Vragenlijst thesis evaluatie

### 2015-08-19 doc/template/nash.tex
finaal

The benefit formula obtained in the previous chapter is as follows:
\begin{equation}
\beta_{D}(\delta_{D},\delta_{A}) = 1 - \dfrac{k_{D}}{\delta_{D}}
\end{equation}

@@

\subsection*{Case B: $ d \leq\delta_{D} \leq \delta_{A} + d$}
The defender's benefit formula obtained in the previous chapter in this case is as follows:
\begin{equation*}
\beta_{D}(\delta_{D},\delta_{A}) = 1 - \dfrac{\delta_{D}}{2\delta_{A}} - \dfrac{d^{2}}{2\delta_{D}\delta_{A}} + \dfrac{d}{\delta_{A}}  - \dfrac{k_{D}}{\delta_{D}}
\end{equation*}

@@

The benefit formula for the defender obtained in the previous chapter in this case is as follows:
\begin{equation*}
\beta_{D}(\delta_{D},\delta_{A})= \dfrac{\delta_{A}}{2\delta_{D}} + \dfrac{d}{\delta_{D}} - \dfrac{k_{D}}{\delta_{D}} = \dfrac{\delta_{A} + 2 (d-k_{D})}{2\delta_{D}}
\end{equation*}

@@

For $\delta_{A} + 2(d-k_{D}) > 0$ the benefit will be always positive but decreasing, see figure \ref{ShapeUp}. 
The defender will always play as fast as he can if $\delta_{A} + 2(d-k_{D}) > 0$ for $k_{D} < d$ or $k_{D} > d$ because $\delta_{A}$ will be positive in either case. There is an edge case if $d=k_{D}$, which results in a benefit of $\beta_{D}(\delta_{D},\delta_{A})= \dfrac{\delta_{A}}{2\delta_{D}}$. \\
\begin{figure}
\centering
\includegraphics[scale=0.5]{Images/ShapesUp.png} 
\caption{The benefit function is of the shape of 1/x and is always decreasing if $\delta_{A} + 2(d-k_{D}) > 0$. }
\label{ShapeUp}
\end{figure}

@@

\subsection{Best Responses of $\delta_{D}$}
The optimum functions will be piecewise functions. We distinguish six cases for different values of $\delta_{A}$ depending on the values of $k_{D}$ and $d$. 
%We point out that $\delta_{A}$ and $\delta_{D}$ are positive rates. 
Figure XXX shows on the left how the three cases can be combined in a single continuous function (shown as the thick line). On the right, the derivative function indicates at which points the benefit will change. It is interesting to note that the derivative is also continuous, meaning that the benefit function is smooth and has no rough edges or corners. This implies that there are no sudden changes in benefit for small changes of period.

\subsection*{$\delta_{A} < 2(k_{D} - d)$}
For case A, the function will always increase if $k_{D} > 0$. If $k_{D} < 0$ it means that the cost is negative and we assume a positive cost. The function will thus never decrease. $k_{D} =0$ is an edge case and will be covered later in the paragraph of edge cases. So for case A we can conclude that the function is always increasing. In the next case, case B, the benefit function will increase in the interval $[0, 2(k_{D}-d)[$. In case C, for $\delta_{A} < 2(k_{D} - d)$, the benefit function will always increase. Because for all the cases we are dealing with a negative benefit function that is increasing, the maximum benefit is achieved for $\delta_{} = \infty$. This can be seen in (A) in figure \ref{case1D}.

@@

\subsection*{$\delta_{A} = 2(k_{D} - d)$}
The delay can not be a negative value. So for $\delta_{A}$, a positive period, to be equal to  $2(k_{D} - d)$, $k_{D}$ has to be positive. \\
For case A, if $k_{D}>0$ the benefit function is always increasing. In case B, the value of $\delta_{A} =2(k_{D} - d)$ has to filled in in the root, $\sqrt{2k_{D}\delta_{A} + d^{2}}$. This gives the value $2k_{D}-d$. $2(k_{D}-d) < 2k_{D}-d$ so this means that $\delta_{A}$ is smaller than $ \sqrt{2k_{D}\delta_{A} + d^{2}}$, so the function is increasing. A maximum is achieved for $\delta_{D}$ equal to the maximum of $\left\lbrace \delta_{A}+d, \sqrt{2k_{D}\delta_{A} + d^{2}}\right\rbrace $. If we fill in $\delta_{A} = 2(k_{D} - d)$, the two values are the same so they are both a maximum.
If we fill in the value of $\delta_{A} = 2(k_{D} - d)$ in case C, the benefit will always be 0. Case C is the case for all values $\delta_{D} \geq \delta_{A} + d$, so $\beta_{D}=0$ is true for all $\delta_{D} \in [\delta_{A}+d, \infty]$.
The defender's maximum benefit is thus achieved for all $\delta_{D} \in [\sqrt{2k_{D}\delta_{A} + d^{2}}, \infty]$. See (B) in figure \ref{case1D}.

@@

\subsection*{$k_{D}=0$}
The cost of flipping for the defender is equal to zero. If we look at the benefit function of the defender and it's derivative in figure \ref{cost0}, we can see that the benefit for case B increases until $d$ and that the benefit in case A stays the same until $d$. After point $d$ the benefit decreases in all the cases.

\begin{figure}[hbtp]
\centering
\includegraphics[scale=1]{Images/cost0.pdf} 
\caption{Benefit function and derivative for a cost $k_{D} = 0$ and with $d (=2)$ and $\delta_{A}=(1.5)$ not equal to zero.}
\label{cost0}
\end{figure}

@@

The benefit formula for the attacker for this case obtained in the previous chapter is as follows:
\begin{equation}
\beta_{A}(\delta_{D},\delta_{A}) =  - \dfrac{k_{A}}{\delta_{A}}
\end{equation}

@@

\subsection*{Case B: $ \delta_{A} \leq \delta_{D} -d$ }
The benefit formula for the attacker for this case obtained from the previous chapter is as follows:
\begin{equation*}
\beta_{A}(\delta_{D},\delta_{A}) =1- \dfrac{\delta_{A}}{2\delta_{D}} - \dfrac{k_{A}}{\delta_{A}} - \dfrac{d}{\delta_{D}}
\end{equation*}
The derivative for a fixed $\delta_{D}$ is as follows:
\begin{equation*}
\dfrac{\partial \beta_{A}(\delta_{D},\delta_{A})}{\partial \delta_{A}} = \dfrac{-1}{2\delta_{D}} + \dfrac{k_{A}}{\delta_{A}^{2}}
\end{equation*}
The stationary points (maximum, minimum) can be found by setting the first derivative equal to zero and finding the roots of the resulting equation:
\begin{equation*}
\frac{\partial \beta_{A}(\delta_{D},\delta_{A})}{\partial \delta_{D}} =0 ~~~~~~ =>~~~~~~ \delta_{A} = \sqrt{2\delta_{D}k_{A}}
\end{equation*}
It follows that $\beta_{A}(\delta_{D},\cdot)$ is increasing on $[0,\sqrt{2k_{A}\delta_{D}}]$ and decreasing on $[\sqrt{2k_{A}\delta_{D}}, \infty]$ and thus has a maximum on $\delta_{A} = minimum \{\delta_{D} -d, \sqrt{2k_{A}\delta_{D}} \} $. The minimum between $\delta_{D}-d$ and $ \sqrt{2k_{A}\delta_{D}}$ is needed because $\delta_{A} $ cannot exceed $\delta_{D}-d$ in this case. \\

@@

The benefit formula for the attacker for this case obtained in the previous chapter is as follows:
\begin{equation*}
\beta_{A}(\delta_{D},\delta_{A}) =\dfrac{\delta_{D}}{2\delta_{A}} - \dfrac{k_{A}}{\delta_{A}} + \dfrac{d^{2}}{2\delta_{D}\delta_{A}} - \dfrac{d}{\delta_{A}}
\end{equation*}
The derivative for a fixed $\delta_{D}$ is as follows:
\begin{equation*}
\dfrac{\partial \beta_{A}(\delta_{D},\delta_{A})}{\partial \delta_{A}} = -\dfrac{\delta_{D}}{2\delta_{A}^{2}} + \dfrac{k_{A}}{\delta_{A}^{2}} - \dfrac{d^{2}}{2\delta_{D}\delta_{A}^{2}} + \dfrac{d}{\delta_{A}^{2}} = \dfrac{-\delta_{D}^{2} - d^{2} + 2\delta_{D}d + 2\delta_{D}k_{A}}{2\delta_{A}^{2}\delta_{D}}
\end{equation*}
The stationary points (maximum, minimum) can be found by setting the first derivative equal to zero and finding the roots of the resulting equation:
\begin{equation*}
\frac{\partial \beta_{A}(\delta_{D},\delta_{A})}{\partial \delta_{D}} =0 ~~~~~~ =>~~~~~~  \delta_{D}^{2}-\delta_{D}(2k_{A}-2d) + d^{2}= 0
\end{equation*}

The roots of this quadratic equation are $\delta_{D}=d+k_{A}\pm \sqrt{2dk_{A}+k_{A}^{2}}$. Because for this case $d\leq \delta_{D}$, we only look at root $\delta_{D}=d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$. $\sqrt{2dk_{A}+k_{A}^{2}}$ is bigger than $k_{A}$ so if we subtract it from $d+k_{A}$, we are in the part where $delta_{D}$ is smaller than d. \\
It follows that $\beta_{A}(\delta_{D},\delta_{A})$ is increasing and non-positive if $\delta_{D}> d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$ and decreasing and positive if $\delta_{D} < d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$. \\

@@

\subsubsection*{$\delta_{D} < d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$} 
For case B, the function is increasing. The function has a maximum on on $\delta_{A} = minimum \{\delta_{D} -d, \sqrt{2k_{A}\delta_{D}} \} $. For $\delta_{D} < d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$, the minimum of the two values is $\delta_{D}-d$.\\
For case C, if $\delta_{D} < d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$, the benefit function is increasing. Because we have a continuous function and the benefit is still increasing and negative in case C, the defender will try not to play. The defender's optimum benefit is achieved in $\delta_{A}=\infty$. See (A) in figure \ref{case1A}.

\begin{figure}[hbtp]
\centering
\includegraphics[scale=1]{Images/case1A.pdf}
\caption{ Illustration of the best response functions. The left functions are the piecewise benefit function of the attacker for a certain values of $k_{A},d$ and $\delta_{D}$. The right functions are the derivatives of the benefit functions on the left. The best responses are the values where the function intersects with the x-as. (A): $\delta_{D} > d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$, (B): $\delta_{D} = d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$, (C): $\delta_{D} < d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$}.
\label{case1A}
\end{figure}

@@

%The benefit $\beta_{A}(\delta_{D},\delta_{A})=0$ for case 1 and case 2.b for all $\delta_{D}$ in $[0, \infty [$. For case 2.a it follows that the benefit is increasing. The attacker's maximum benefit is achieved at any $\delta_{A} $ in 
\subsubsection*{$\delta_{D} > d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$} 
For case B, the function is increasing. The function has a maximum on on $\delta_{A} = minimum \{\delta_{D} -d, \sqrt{2k_{A}\delta_{D}} \} $. For $\delta_{D} > d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$, the minimum of the two values is $\delta_{D}-d$.\\
For case C, if $\delta_{D} > d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$ the function is decreasing. So the optimum benefit for all the cases is when $\delta_{D} = \delta_{D}-d$. See (C) in figure \ref{case1A}.\\
%For case 1 and case 2.b the benefit is increasing but non-positive. This means that the attacker won't play ($\delta_{A} = \infty$).

@@

\subsection*{$k_{A}=0$}
If the cost of playing for the attacker is zero, the attacker can play as fast as he can.  If $\delta_{D} \leq d$, looking at the benefit formula for the attacker, it does not matter what the attacker does, his benefit will always be zero. He will play with a rate $\delta_{A} \in [0,\infty ]$.  We can merge this with the previous case where $\delta_{D}=0$ and $k_{A}=0$.  If $\delta_{D} > d$, the attacker will play. He will play with a rate of $\delta_{A} \in [0, \delta_{D} - d ]$. 
\subsection*{$\delta_{D}=0$}
If $\delta_{D}=0$ it follows from the case $\delta_{D} \leq d$ that the attacker will always have a negative benefit, unless the cost is zero. If the cost is zero we have again the case of $\delta_{D}=0$ and $k_{A}=0$. But if the cost is non-zero, the optimal strategy of the defender is not moving at all.

@@

 \begin{displaymath}
  opt_{A}(\delta_{D}) = \left\{
     \begin{array}{lr}
     \infty & \delta_{D} = 0 \\
     \left[0,\infty\right] & \delta_{D} \leq d ~~\& ~~k_{A}=0 \\
          \left[0,\delta_{D} - d\right] & \delta_{D} > d ~~\& ~~k_{A}=0 \\
            \infty & \delta_{D} < d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}} \\
       \left[ \delta_{D}-d, \infty\right],  & \delta_{D} = d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}} \\
    	\delta_{D}-d, & \delta_{D} > d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}
     \end{array}
   \right.
\end{displaymath}
\\

@@

The Nash Equilibria can be found as the intersection points of the piecewise functions $opt_{A}(\delta_{D})$ and $opt_{D}(\delta_{A})$. For this we have to compare the function in terms of the relationship of the players move cost. %We distinguish three cases: $k_{A} < k_{D} , ~k_{A} > k_{D} $ and $k_{A} = k_{D}$.

>>>>

The benefit formula for this case corresponds with the first piece of the benefit function of the defender obtained in the previous chapter:
\begin{equation}
\beta_{D}(\delta_{D},\delta_{A}) = 1 - \dfrac{k_{D}}{\delta_{D}}
\end{equation}

@@

\subsection*{Case B: $ d \leq\delta_{D} \leq \delta_{A} + d$}
The benefit formula for this case corresponds with the second piece of the benefit function of the defender obtained in the previous chapter:
\begin{equation*}
\beta_{D}(\delta_{D},\delta_{A}) = 1 - \dfrac{\delta_{D}}{2\delta_{A}} - \dfrac{d^{2}}{2\delta_{D}\delta_{A}} + \dfrac{d}{\delta_{A}}  - \dfrac{k_{D}}{\delta_{D}}
\end{equation*}

@@

The benefit formula for this case corresponds with the third piece of the benefit function of the defender obtained in the previous chapter:
\begin{equation*}
\beta_{D}(\delta_{D},\delta_{A})= \dfrac{\delta_{A}}{2\delta_{D}} + \dfrac{d}{\delta_{D}} - \dfrac{k_{D}}{\delta_{D}} = \dfrac{\delta_{A} + 2 (d-k_{D})}{2\delta_{D}}
\end{equation*}

@@

For $\delta_{A} + 2(d-k_{D}) > 0$ the benefit will always be positive but decreasing, see figure \ref{ShapeUp}. 
The defender will always play as fast as he can if $\delta_{A} + 2(d-k_{D}) > 0$ for $k_{D} < d$ or $k_{D} > d$ because $\delta_{A}$ will be positive in either case. \\
\begin{figure}
\centering
\includegraphics[scale=0.5]{Images/ShapesUp.png} 
\caption{The benefit function is of the shape of 1/x and is always decreasing if $\delta_{A} + 2(d-k_{D}) > 0$. }
\label{ShapeUp}
\end{figure}

@@

\subsection{Best Responses of $\delta_{D}$}
The optimum functions are piecewise functions. We distinguish three cases for different values of $\delta_{A}$ depending on the values of $k_{D}$ and $d$. 
%We point out that $\delta_{A}$ and $\delta_{D}$ are positive rates. 
Figure \ref{cost0} shows on the left how the three cases can be combined in a single continuous function (shown as the thick line). On the right, the derivative function indicates at which points the benefit will change. It is interesting to note that the derivative is also continuous, meaning that the benefit function is smooth and has no rough edges or corners. This implies that there are no sudden changes in benefit for small changes of period. The points that are interesting to look at are the points of the derivative function that intersect with the x-axis ($\delta_{A}$). These points are the roots of the derivative function and show where the benefit function is increasing or decreasing and therefore give the value of the maximum benefit of the defender. 
\begin{figure}[hbtp]
\centering
\includegraphics[scale=1]{Images/cost0.pdf} 
\caption{Benefit function and derivative for a cost $k_{D} = 0$ and with $d (=2)$ and $\delta_{A}=(1.5)$ not equal to zero.}
\label{cost0}
\end{figure}
\subsection*{$\delta_{A} < 2(k_{D} - d)$}
For case A, the function is increasing if $k_{D} > 0$. If $k_{D} < 0$ the function is decreasing but a positive cost is assumed. The function will therefore never decrease. $k_{D} =0$ is an edge case and will be covered later in the paragraph of edge cases. So for case A we can conclude that the function is always increasing. In the next case, case B, the benefit function will increase in the interval $[0, 2(k_{D}-d)]$. In case C, for $\delta_{A} < 2(k_{D} - d)$, the benefit function will always increase. Case B and case C are both increasing and both functions are negative. The benefit will never become positive as such, the defender will try to not to play. The maximum benefit is achieved for $\delta_{} = \infty$. This can be seen in (A) in figure \ref{case1D}.

@@

\subsection*{$\delta_{A} = 2(k_{D} - d)$}
The delay can not be a negative value. So for $\delta_{A}$, a positive period, to be equal to  $2(k_{D} - d)$, $k_{D}$ has to be positive. \\
For case A, if $k_{D}>0$ the benefit function is always increasing. In case B, the value of $\delta_{A} =2(k_{D} - d)$ has to be filled in the root, $\sqrt{2k_{D}\delta_{A} + d^{2}}$. This gives the value $2k_{D}-d$. $2(k_{D}-d) < 2k_{D}-d$ so this means that $\delta_{A}$ is smaller than $ \sqrt{2k_{D}\delta_{A} + d^{2}}$, so the function is increasing. A maximum is achieved for $\delta_{D}$ equal to the maximum of $\left\lbrace \delta_{A}+d, \sqrt{2k_{D}\delta_{A} + d^{2}}\right\rbrace $. If we fill in $\delta_{A} = 2(k_{D} - d)$, the two formulas have the same result so they are both a maximum.
If we fill in the value of $\delta_{A} = 2(k_{D} - d)$ in case C, the benefit will always be 0. Case C is the case for all values $\delta_{D} -d \geq \delta_{A}$, so $\beta_{D}=0$ is true for all $\delta_{D} \in [\delta_{D}-d, \infty]$.
The defender's maximum benefit is thus achieved for all $\delta_{D} \in [\delta_{D}-d, \infty]$. See (B) in figure \ref{case1D}.

@@

\subsection*{$k_{D}=0$}
The cost of flipping for the defender is equal to zero. If we look at the benefit function of the defender and it's derivative in figure \ref{cost0}, we can see that the benefit for case B increases until $d$ and that the benefit in case A stays the same until $d$. After point $d$ the benefit decreases in all the cases. So the period of the defender will be equal to $\delta_{D} \in [0,d]$.

@@

The benefit formula for this case corresponds with the first piece of the benefit function of the attacker obtained in the previous chapter:
\begin{equation}
\beta_{A}(\delta_{D},\delta_{A}) =  - \dfrac{k_{A}}{\delta_{A}}
\end{equation}

@@

\subsection*{Case B: $ \delta_{A} \leq \delta_{D} -d$ }
The benefit formula for this case corresponds with the second piece of the benefit function of the attacker obtained in the previous chapter:
\begin{equation*}
\beta_{A}(\delta_{D},\delta_{A}) =1- \dfrac{\delta_{A}}{2\delta_{D}} - \dfrac{k_{A}}{\delta_{A}} - \dfrac{d}{\delta_{D}}
\end{equation*}
The derivative for a fixed $\delta_{D}$ is as follows:
\begin{equation*}
\dfrac{\partial \beta_{A}(\delta_{D},\delta_{A})}{\partial \delta_{A}} = \dfrac{-1}{2\delta_{D}} + \dfrac{k_{A}}{\delta_{A}^{2}}
\end{equation*}
The stationary points (maximum, minimum) can be found by setting the first derivative equal to zero and finding the roots of the resulting equation:
\begin{equation*}
\frac{\partial \beta_{A}(\delta_{D},\delta_{A})}{\partial \delta_{D}} =0 ~~~~~~ =>~~~~~~ \delta_{A} = \sqrt{2\delta_{D}k_{A}}
\end{equation*}
It follows that $\beta_{A}(\delta_{D},\cdot)$ is increasing on $[0,\sqrt{2k_{A}\delta_{D}}]$ and decreasing on $[\sqrt{2k_{A}\delta_{D}}, \infty]$ and thus has a maximum on $\delta_{A} = minimum \{\delta_{D} -d, \sqrt{2k_{A}\delta_{D}} \} $. The minimum between $\delta_{D}-d$ and $ \sqrt{2k_{A}\delta_{D}}$ is needed because $\delta_{A} $ cannot exceed $\delta_{D}-d$ in this case. \\

@@

The benefit formula for this case corresponds with the third piece of the benefit function of the attacker obtained in the previous chapter:
\begin{equation*}
\beta_{A}(\delta_{D},\delta_{A}) =\dfrac{\delta_{D}}{2\delta_{A}} - \dfrac{k_{A}}{\delta_{A}} + \dfrac{d^{2}}{2\delta_{D}\delta_{A}} - \dfrac{d}{\delta_{A}}
\end{equation*}
The derivative for a fixed $\delta_{D}$ is as follows:
\begin{equation*}
\dfrac{\partial \beta_{A}(\delta_{D},\delta_{A})}{\partial \delta_{A}} = -\dfrac{\delta_{D}}{2\delta_{A}^{2}} + \dfrac{k_{A}}{\delta_{A}^{2}} - \dfrac{d^{2}}{2\delta_{D}\delta_{A}^{2}} + \dfrac{d}{\delta_{A}^{2}} = \dfrac{-\delta_{D}^{2} - d^{2} + 2\delta_{D}d + 2\delta_{D}k_{A}}{2\delta_{A}^{2}\delta_{D}}
\end{equation*}
The stationary points (maximum, minimum) can be found by setting the first derivative equal to zero and finding the roots of the resulting equation:
\begin{equation*}
\frac{\partial \beta_{A}(\delta_{D},\delta_{A})}{\partial \delta_{D}} =0 ~~~~~~ =>~~~~~~  \delta_{D}^{2}-\delta_{D}(2k_{A}-2d) + d^{2}= 0
\end{equation*}

The roots of this quadratic equation are $\delta_{D}=d+k_{A}\pm \sqrt{2dk_{A}+k_{A}^{2}}$. Because for this case $d\leq \delta_{D}$, we only look at root $\delta_{D}=d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$. $\sqrt{2dk_{A}+k_{A}^{2}}$ is bigger than $k_{A}$ so if we subtract it from $d+k_{A}$, we are in the part where $\delta_{D}$ is smaller than \textit{d}. \\
It follows that $\beta_{A}(\delta_{D},\delta_{A})$ is increasing and non-positive if $\delta_{D}> d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$ and decreasing and positive if $\delta_{D} < d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$. \\

@@

\subsubsection*{$\delta_{D} < d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$} 
For case B, the function is increasing. The function has a maximum on $\delta_{A} = minimum \{\delta_{D} -d, \sqrt{2k_{A}\delta_{D}} \} $. For $\delta_{D} < d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$, the minimum of the two values is $\delta_{D}-d$.\\
For case C, if $\delta_{D} < d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$, the benefit function is increasing. Because we have a continuous function and the benefit is still increasing and negative in case C, the defender will try not to play. The defender's optimum benefit is achieved in $\delta_{A}=\infty$. See (A) in figure \ref{case1A}.

\begin{figure}[hbtp]
\centering
\includegraphics[scale=1]{Images/case1A.pdf}
\caption{ Illustration of the best response functions. The left functions are the piecewise benefit function of the attacker for a certain values of $k_{A},d$ and $\delta_{D}$. The right functions are the derivatives of the benefit functions on the left. The best responses are the values where the function intersects with the x-axis. (A): $\delta_{D} < d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$, (B): $\delta_{D} = d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$, (C): $\delta_{D} > d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$}.
\label{case1A}
\end{figure}

@@

%The benefit $\beta_{A}(\delta_{D},\delta_{A})=0$ for case 1 and case 2.b for all $\delta_{D}$ in $[0, \infty [$. For case 2.a it follows that the benefit is increasing. The attacker's maximum benefit is achieved at any $\delta_{A} $ in 
\subsubsection*{$\delta_{D} > d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$} 
For case B, the function is increasing. The function has a maximum on $\delta_{A} = minimum \{\delta_{D} -d, \sqrt{2k_{A}\delta_{D}} \} $. For $\delta_{D} > d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$, the minimum of the two values is $\delta_{D}-d$.\\
For case C, if $\delta_{D} > d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$ the function is decreasing. So the optimum benefit for all the cases is when $\delta_{D} = \delta_{D}-d$. See (C) in figure \ref{case1A}.\\
%For case 1 and case 2.b the benefit is increasing but non-positive. This means that the attacker won't play ($\delta_{A} = \infty$).

@@

\subsection*{$k_{A}=0$}
If the cost of playing for the attacker is zero, the attacker can play as fast as he can.  If $\delta_{D} \leq d$, looking at the benefit formula for the attacker, it does not matter what the attacker does, his benefit will always be zero. He will play with a rate $\delta_{A} \in [0,\infty ]$.  We can merge this with the previous case where $\delta_{D}=0$ and $k_{A}=0$.  If $\delta_{D} > d$, the attacker will play as fast as he can. He will play with a rate of $\delta_{A} =0$. 
\subsection*{$\delta_{D}=0$}
If $\delta_{D}=0$ it follows from the case $\delta_{D} \leq d$ that the attacker will always have a negative benefit, unless the cost is zero. If the cost is zero we have again the case of $\delta_{D}=0$ and $k_{A}=0$. But if the cost is non-zero, the optimal strategy of the defender is not moving at all.

@@

 \begin{displaymath}
  opt_{A}(\delta_{D}) = \left\{
     \begin{array}{lr}
     \infty & \delta_{D} = 0 \\
     \left[0,\infty\right] & \delta_{D} \leq d ~~\& ~~k_{A}=0 \\
         0 & \delta_{D} > d ~~\& ~~k_{A}=0 \\
            \infty & \delta_{D} < d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}} \\
       \left[ \delta_{D}-d, \infty\right],  & \delta_{D} = d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}} \\
    	\delta_{D}-d, & \delta_{D} > d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}
     \end{array}
   \right.
\end{displaymath}
\\

@@

  %We distinguish three cases: $k_{A} < k_{D} , ~k_{A} > k_{D} $ and $k_{A} = k_{D}$.
